---
title: "Assignment_5"
author: "Felix Froschauer"
date: "29 12 2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## General Setup
First of all, we need to import all necessary libraries and set up the working directory correctly.


```{r library, message=FALSE, warning=FALSE}
library(httr)
library(jsonlite)
library(ggplot2)
library(readr)
library(dplyr)
```

## Exercise 1 - Setting up a new GitHub repository

The whole assignment can be accessed publicly using the following link: [https://github.com/froschauerfelix/dspm_5](https://github.com/froschauerfelix/dspm_5)

## Exercise 2 - Getting to know the API

When you are sharing your code, the personalized API-Key should stay hidden. To achieve that, the API-Key can be imported using another file and only in that specific file, the API-Key can be detected. Having the API-Key imported into our file, it can be used to send the first get-requests.


```{r API_key}

source("~/R/DS ProjectManagement/Assignment 5/API_key.R")
```

## Exercise 3 - Interacting with the API - the basics

After sending the first request, the status of the response needs to be reviewed. 
Here: The status is 200. Everything is working fine.

```{r cars, echo=FALSE}
# complete list of venues in Germany (Only page 1)
venues_response <- GET(paste(
  "https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=DE&apikey", 
  api_key, sep = "="))
venues_list <- jsonlite::fromJSON(
  content(venues_response, as = "text"))[["_embedded"]][["venues"]]
venues_response
```
A single get-request leads to a data set with 20 different venues. Only the first page is accessed here and to access more data, more requests need to be send. 


```{r name, echo=FALSE}
size <- 20
df_venues_de_page_1 <- 
  data.frame(
    name = character(size), 
    city = character(size), 
    postalcode = integer(size), 
    address = character(size),
    url = character(size), 
    long = integer(size), 
    lat = integer(size))


# complete list of venues in Germany (Only page 1)
venues_response <- GET(paste(
  "https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=DE&apikey", 
  api_key, sep = "="))
venues_list <- jsonlite::fromJSON(
  content(venues_response, as = "text"))[["_embedded"]][["venues"]]

# insert data from venues to data frame
df_venues_de_page_1$name <- venues_list$name
df_venues_de_page_1$city <- venues_list$city$name
df_venues_de_page_1$postalcode <- venues_list$postalCode
df_venues_de_page_1$address <- venues_list$address$line1
df_venues_de_page_1$url <- venues_list$url 
df_venues_de_page_1$long<- venues_list$location$longitude
df_venues_de_page_1$lat<- venues_list$location$latitude

glimpse(df_venues_de_page_1)
```

## Exercise 4 - Interacting with the API - advanced

Iterating through all pages takes time. For that reason, I have saved all venues in Germany in a .csv file and the iteration doesn't need to be executed for each separate working session. The data can be updated in a separate file, so that it's always up to date. The code can be viewed in the [github repository](https://github.com/froschauerfelix/dspm_5) in the file `get_all_data.R`.


```{r  venues_ger, echo=FALSE, message=FALSE} 
# import the correct csv file
country_code <- "de"

# file with data generating process
df_venues <- read_csv(paste(paste("df_venues",country_code,sep="_"), "csv", sep="."))

glimpse(df_venues)
```

# Exercise 5 - Visualizing the extracted data

Not every venue location can be plotted. Wrong latitude and longitude values need to be filtered and  missing values (for long and lat) need to be excluded. Out of the 12560 observations about 8099 are plotted here (29. December).

```{r plot_ger, echo=FALSE}
country <- "Germany"
# correct type
df_venues$long <- as.numeric(df_venues$long)
df_venues$lat <- as.numeric(df_venues$lat)

# eliminating extreme and missing values
if (country == "Germany"){
subset_venues <- subset(df_venues, lat > 47.271679)
subset_venues <- subset(subset_venues, lat < 55.0846)

subset_venues <- subset(subset_venues, long > 5.866943)
subset_venues <- subset(subset_venues, as.numeric(long) < 15.043611)
}


if (country == "France") {
  subset_venues <- subset(df_venues, lat > 40)
  subset_venues <- subset(subset_venues, lat < 51.05)
  
  subset_venues <- subset(subset_venues, long > -5.5)
  subset_venues <- subset(subset_venues, as.numeric(long) < 10)
  
}

title <- paste("Event locations across", country, sep=" ")


# plot for specific country
ggplot() +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = country),
    fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = title,caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) +
  geom_point(data = subset_venues, aes(x = long, y = lat), color = "red", size = 0.2) 


```

## Exercise 6 - Event locations in France

Exercises 2 to 5 are repeated here for another country: France.

First page observations:

```{r page_1_fr, echo=FALSE}
venues_response_fr <- GET(paste("https://app.ticketmaster.com/discovery/v2/venues.json?countryCode=FR&apikey", api_key, sep = "="))

# Exercise 3 again
size <- 20
df_venues_fr_page_1 <- 
  data.frame(
    name = character(size), 
    city = character(size), 
    postalcode = integer(size), 
    address = character(size),
    url = character(size), 
    long = integer(size), 
    lat = integer(size))


# complete list of venues (Only page 1)
venues_list_fr <- jsonlite::fromJSON(content(venues_response_fr, as = "text"))[["_embedded"]][["venues"]]

# insert columns to data frame
df_venues_fr_page_1$name <- venues_list_fr$name
df_venues_fr_page_1$city <- venues_list_fr$city$name
df_venues_fr_page_1$postalcode <- venues_list_fr$postalCode
df_venues_fr_page_1$address <- venues_list_fr$address$line1
df_venues_fr_page_1$url <- venues_list_fr$url 
df_venues_fr_page_1$long<- venues_list_fr$location$longitude
df_venues_fr_page_1$lat<- venues_list_fr$location$latitude

glimpse(df_venues_fr_page_1)

```

For all pages:
```{r all_fr, echo=FALSE, message=FALSE}
# import the correct csv file
country_code <- "fr"

# file with data generating process
df_venues <- read_csv(paste(paste("df_venues",country_code,sep="_"), "csv", sep="."))

glimpse(df_venues)

```

Exluding the extreme values for France, the following plot can be drawn.
```{r plot_fr, echo=FALSE}
country <- "France"
# correct type
df_venues$long <- as.numeric(df_venues$long)
df_venues$lat <- as.numeric(df_venues$lat)

# eliminating extreme and missing values
if (country == "Germany"){
subset_venues <- subset(df_venues, lat > 47.271679)
subset_venues <- subset(subset_venues, lat < 55.0846)

subset_venues <- subset(subset_venues, long > 5.866943)
subset_venues <- subset(subset_venues, as.numeric(long) < 15.043611)
}


if (country == "France") {
  subset_venues <- subset(df_venues, lat > 40)
  subset_venues <- subset(subset_venues, lat < 51.05)
  
  subset_venues <- subset(subset_venues, long > -5.5)
  subset_venues <- subset(subset_venues, as.numeric(long) < 10)
  
}

title <- paste("Event locations across", country, sep=" ")


# plot for specific country
ggplot() +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = country),
    fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = title,caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) +
  geom_point(data = subset_venues, aes(x = long, y = lat), color = "red", size = 0.2) 

```

